\section{Discussion: why does birthplace matter?}

Here I examine evidence supporting four mechanisms: (i) culture, norms, and learning, (ii) human capital, (iii) marriage and household formation, and (iv) changes in parental investments.


\subsection{Culture, norms, and learning}

Birthplace effects could reflect internalization or learning of local norms and practices around women's work. Epidemiological research sees country of ancestry FLFP rates as a summary measure that captures variations in preferences, beliefs, and culture that influence aggregate female employment and can be passed down through generations \citep{Fernandez2009}. 


In table \ref{table:table_8}, I use data from the Ethnographic Atlas \citep{Murdock1967} to document that FLFP rates capture meaningful variation in cultural practices and gender norms \textit{within Indonesia}. Columns (1) to (3) show results from regressing the regency's FLFP rates on the prevalence of several traditional or pre-modern norms/practices and other regency characteristics. I include as regressors the prevalence of practices related to gender or marriage, namely matrilocality, emphasis on female chastity, bride price, use of plow agriculture, polygamy, and male-only agriculture. Column (1) shows that these variables are highly significant, and they alone account for 30\% in the variation of FLFP rates. Moreover, columns (2) and  (3) show these variables remain jointly significant when including additional controls, such as the regency's industrial and age structures and overall education levels. In addition,  appendix table \ref{table:table_A5} shows these practices predict other female outcomes such as age at first marriage and number of children. In contrast, columns (4) to (6) in  \ref{table:table_8} show that they have little bite when using the regency's male LFP rate as the outcome.

{\onehalfspacing
	\tftext{\input{\thesispath/results/tables/table_8.tex}}
}


Table \ref{table:table_8}  suggests that women born in high-FLFP regencies are exposed to a distinct set of norms and cultural practices that could impact their choices and preferences. Combined with the importance of late childhood and early adolescence in my main results, this aligns well with evidence from psychology and economics that identifies this period as key for preference formation. Early adolescents are mature enough to form their own opinions but receptive to external influences \citep{Markus1986}. For instance, \cite{Dhar2022} find long-lasting effects from interventions targeting gender views of Indian teenagers, and \cite{Olivettib} show that exposure to classmates' working mothers during secondary has long-term effects on women's work decisions in the US.




\subsection{Human capital}
Exposure to birthplace could affect women's labor supply via their career expectations and their educational investment. Exposure to an environment where women actively participate in economic activities could alter their career expectations and make them more likely to invest in education. For example, \cite{Molina2022} show that in high-FLFP Japanese municipalities, young women exhibit greater educational aspirations, leading to increased investment in schooling. 


However, investment in education is unlikely to account for my results. High-FLFP regencies have worse primary and secondary completion rates (see appendix table \ref{table:table_A6}). Moreover, there is little evidence that women who stay longer in these regencies invest more in education. If schooling drove the patterns observed in figure \ref{fig:figure_3}, I should observe increasing persistence when I use schooling measures as the outcome. Appendix figure \ref{fig:figure_B7} shows no evidence of this when the outcome is the likelihood of completing secondary school. Although the figure suggests an apparent increase in the likelihood of completing primary school, these slopes are imprecise, and I cannot reject that all of them are equal (i.e., null birthplace effects).\footnote{I also cannot reject that all slopes from 8 to 17 are the same. Additionally, the \textit{employment} persistence coefficients remain unchanged when I control for interactions between birthplace FLFP, migration age, and completed primary dummies. If higher employment were mainly due to higher completion rates of primary school, the coefficients in figure \ref{fig:figure_3} should flatten once I control for this triple interaction.}



\subsection{Marriage and household formation}

Previous research emphasizes the interaction between husbands' background and women's labor market choices \citep{Fernandez2004,Blau2011}. In appendix figure \ref{fig:figure_B8} I restrict the sample to women with identified husbands in the Intercensal Survey and test whether high-exposure women choose husbands of certain backgrounds. I focus on five main traits: being an internal migrant, born in above-mean-FLFP regency, high-school graduate, employed, and salaried. If high-exposure women were selecting husbands with different backgrounds, there should be clear trends in the slope estimates. The lack of such pattern in both panels of figure \ref{fig:figure_B8} suggests that women with low and high exposure select partners with similar traits.\footnote{I also studied whether women's choices are affected by the length of their husband's exposure to high-FLFP regencies. Nevertheless, the sample is small and I lack the power to draw any meaningful conclusion.}





\subsection{Changes in parental investment}
{\cite{Molina2022} suggests that exposure to local labor market opportunities influences parental investment in girls' education. There are two main ways through which parental investment could explain my results. Although I cannot fully discard these explanations, they do not seem very plausible in my context.} 


{The first explanation is pure selection. The increasing persistence could reflect that parents who stayed longer in high-FLFP regencies happened to invest more in their children. If parents who stayed longer in high-FLFP regencies invested more in their daughters' education, one would expect that girls from these locations came from families with higher socioeconomic backgrounds. However, panel (d) of figure \ref{fig:figure_6} shows little evidence of selection on parental socioeconomic background. Moreover, since high-FLFP regencies have worse educational outcomes, high-investment parents would likely leave these locations earlier rather than later.}

Another possibility is that staying longer in these locations affected parental investment. However, there is little evidence that staying longer in these locations is associated with higher education. Admittedly, investment could act through channels other than schooling, but changes in investment would need to occur at a very specific time in the children's development to account for my results fully.



\input{paper_elements/new_appendix_sections}






